SpikeIn MSstatsPTM Analysis

### 2022-07-15 code/MSstatsPTM_Simulation_Analysis_new.Rmd
replaced ttest with anova

---
title: "MSstatsPTM Simulation Analysis"
author: "Devon Kohler"
date: "3/7/2022"
output:
  html_document: default
  pdf_document: default
---

@@

To simulate data the `PTMsimulateExperiment()` function from Tsung-Heng's original MSstatsPTM was used. This function allows us to vary the number of conditions, replicates, number of proteins, number of sites per protein, number of spectral features per site/protein, mean log2-abundance of PTM and PROTEIN, deviation from the mean log2-abundance in each group, standard deviation among replicates, and standard deviation among log2-intensities.

>>>>

---
title: "MSstatsPTM Simulation Analysis"
author: "Devon Kohler"
date: "7/14/2022"
output:
  html_document: default
  pdf_document: default
---

@@

To simulate data the `PTMsimulateExperiment()` function was used. This function allows us to vary the number of conditions, replicates, number of proteins, number of sites per protein, number of spectral features per site/protein, mean log2-abundance of PTM and PROTEIN, deviation from the mean log2-abundance in each group, standard deviation among replicates, and standard deviation among log2-intensities.

### 2022-07-15 code/Spike-in_Analysis.Rmd
replaced ttest with anova

combo_plot_df
combo_plot_df[combo_plot_df$Label == 'mix2-mix3'][['trueLog2FC']] <- combo_plot_df[combo_plot_df$Label == 'mix2-mix3'][['trueLog2FC']]*-1

png("../main/images/spike_in_volcano.png", width = 750, height = 500)
combo_plot_df %>% arrange(Model, labeling) %>% 
  filter(abs(log2FC) < Inf & Label %in% c("mix2-mix3", "mix1-mix4", "mix3 vs mix2",
                                          "mix4 vs mix1")) %>%
  ggplot(aes(log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.2, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  geom_vline(aes(xintercept = trueLog2FC),color = "darkred", linetype= "dashed") +
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ Model + contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  scale_y_continuous(limits = c(0,3)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) +
  labs(title = "SpikeIn VolcanoPlot", x= "Log2FC")
dev.off()

@@

### T-Test

Finally we will look at the t-test results.

Again we look at the volcano plots. The spike-in peptides are colored red and their expected log Fold Change is indicated in the subplot title. The background peptides are colored grey and should all be insignificant.

```{r, echo=FALSE, fig.width = 10, fig.height = 7}
load(file = "../data/Spike_in_ttest_model.rda")#ttest_final_model

## Update some naming conventions
ttest_final_model[ttest_final_model$label == 'mix1-mix2'][['contrast_truth']] <- "LogFC: -1 (mix2-mix1)"
ttest_final_model[ttest_final_model$label == 'mix1-mix3'][['contrast_truth']] <- "LogFC: 1 (mix3-mix1)"
ttest_final_model[ttest_final_model$label == 'mix1-mix4'][['contrast_truth']] <- "LogFC: 0 (mix4-mix1)"
ttest_final_model[ttest_final_model$label == 'mix2-mix3'][['contrast_truth']] <- "LogFC: 2 (mix3-mix2)"
ttest_final_model[ttest_final_model$label == 'mix2-mix4'][['contrast_truth']] <- "LogFC: 1 (mix4-mix2)"
ttest_final_model[ttest_final_model$label == 'mix3-mix4'][['contrast_truth']] <- "LogFC: -1 (mix4-mix3)"

ttest_final_model[ttest_final_model$labeling == 'light'][['labeling']] <- "Background Peptides"
ttest_final_model[ttest_final_model$labeling == 'heavy'][['labeling']] <- "SpikeIn Peptides"

ttest_final_model$log2FC <- ttest_final_model$estimate

ttest_final_model$trueLog2FC=ttest_final_model$trueLog2FC*-1
ttest_final_model[ttest_final_model$label == 'mix1-mix2'][['trueLog2FC']] <- ttest_final_model[ttest_final_model$label == 'mix1-mix2'][['trueLog2FC']]*-1
ttest_final_model[ttest_final_model$label == 'mix3-mix4'][['trueLog2FC']] <- ttest_final_model[ttest_final_model$label == 'mix3-mix4'][['trueLog2FC']]*-1
ttest_final_model[ttest_final_model$label == 'mix1-mix3'][['trueLog2FC']] <- ttest_final_model[ttest_final_model$label == 'mix1-mix3'][['trueLog2FC']]*-1

ttest_final_model$contrast_truth = factor(ttest_final_model$contrast_truth, 
                                          levels = 
                                  c("LogFC: -1 (mix2-mix1)",
                                    "LogFC: 1 (mix3-mix1)",
                                    "LogFC: 0 (mix4-mix1)",
                                    "LogFC: 2 (mix3-mix2)",
                                    "LogFC: 1 (mix4-mix2)",
                                    "LogFC: -1 (mix4-mix3)"))

# Volcano plot
png("../supplementary/sim_new/spike_in_ttest_volcano.png", width = 750, height = 500)
ttest_final_model %>% arrange(labeling) %>% 
  filter(abs(log2FC) < Inf) %>%
  ggplot(aes(log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.1, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = 0) + 
  geom_vline(aes(xintercept = trueLog2FC),color = "darkred", linetype= "dashed") +
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 14), 
       axis.text.y = element_text(size = 14), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  scale_y_continuous(limits = c(0,1.5)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) + 
  labs(title = "T-test VolcanoPlot")
dev.off()
```

The results of the t-test are the weakest of the models we have observed. Both before and after adjustment we see no significant results. This may be due to an increased variance in the models, as each t-test model must be fit between two conditions and cannot share information. Additionally we only have two observations per condition, thus if one observation is missing the t-test model breaks down and the model cannot be fit.

To get a closer look at the effect of the adjustment we will look at the volcano plots using the unadjusted pvalue.

``` {r, echo=FALSE, fig.width = 10, fig.height = 7}
# Volcano plot
ttest_final_model %>% arrange(desc(labeling)) %>% 
  filter(abs(estimate) < Inf & label %in% c("mix1-mix3", "mix1-mix4", "mix2-mix3", "mix2-mix4")) %>%
  ggplot(aes(estimate, -log10(pval))) + 
  geom_point(aes(color = labeling, alpha = labeling)) + 
  scale_color_manual(values = c("#D55E00", "#999999")) + 
  scale_alpha_manual(values = c(1, 0.1)) + 
  scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  geom_vline(xintercept = c(1, -1), color = "darkred", linetype = "dashed") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(legend.position = "bottom") + 
  labs(title = "T-test VolcanoPlot: Unadjusted Pvalue")
```

The unadjusted pvalue volcano plots look very similar to what we have seen in the previous two models. The false positives decrease and the spike-in peptides follow the expected FC closer after adjustment.

@@

# Volcano plot
png("../supplementary/sim_new/spike_in_ttest_volcano.png", width = 750, height = 500)
anova_results %>% arrange(labeling) %>% 
  filter(is.finite(log2FC)) %>%
  ggplot(aes(log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.1, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = 0) + 
  geom_vline(aes(xintercept = trueLog2FC),color = "darkred", linetype= "dashed") +
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 14), 
       axis.text.y = element_text(size = 14), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  # scale_y_continuous(limits = c(0,1.5)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) + 
  labs(title = "Anova VolcanoPlot")
dev.off()
```

```{r}

limma_comp = limma_plot_df %>% filter(protadj == "protein adjustment") %>% select(PTM, Label, Log2FC)
anova_comp = anova_results %>% filter(protadj == "protein adjustment") %>% select(ptm, label, log2FC)

comp = merge(limma_comp, anova_comp, by.x = c("PTM", "Label"), by.y = c("ptm", "label"))
comp$diff = comp$Log2FC - comp$log2FC

comp %>% ggplot() + geom_histogram(aes(diff)) + facet_grid(~Label)

limma_comp = limma_plot_df %>% filter(protadj == "no adjustment") %>% select(PTM, Label, Log2FC)
anova_comp = anova_results %>% filter(protadj == "no adjustment") %>% select(ptm, label, log2FC)

comp = merge(limma_comp, anova_comp, by.x = c("PTM", "Label"), by.y = c("ptm", "label"))
comp$diff = comp$Log2FC - comp$log2FC

comp %>% ggplot() + geom_histogram(aes(diff)) + facet_grid(~Label)

@@

ttest_final_model[, log2FC:=NULL]
unadj_spike_ttest <- ttest_final_model %>% filter(labeling == "SpikeIn Peptides" & protadj == "no adjustment")
unadj_spike_ttest <- setNames(unadj_spike_ttest, c("ptm", "Label", "pval", "tstat", "SE", 
                                                   "df", "log2FC", "labeling", "adj.pvalue", 
                                                   "trueLog2FC", "contrast_truth", "protadj"))

unadj_spike_ttest$Adjustment <- "no adjustment"
unadj_spike_ttest$Model <- "T-test"

adj_spike_ttest <- ttest_final_model %>% filter(labeling == "SpikeIn Peptides" & protadj != "no adjustment")
adj_spike_ttest <- setNames(adj_spike_ttest, c("ptm", "Label", "pval", "tstat", "SE", 
                                                   "df", "log2FC", "labeling", "adj.pvalue", 
                                                   "trueLog2FC", "contrast_truth", "protadj"))
adj_spike_ttest$Adjustment <- "protein adjustment"
adj_spike_ttest$Model <- "T-test"

unadj_spike_limma <- limma_model$PTM.Model %>% filter(labeling == "heavy")
unadj_spike_limma <- setNames(unadj_spike_limma, c("PTM", "Label", "log2FC", "pvalue", "df", 
                                                   "se", "labeling", "adj.pvalue", 
                                                   "trueLog2FC", "contrast_truth", "protadj"))
unadj_spike_limma$Adjustment <- "no adjustment"
unadj_spike_limma$Model <- "Limma"
adj_spike_limma <- limma_model$ADJUSTED.Model %>% filter(labeling == "heavy")
adj_spike_limma <- setNames(adj_spike_limma, c("PTM", "Label", "log2FC", "pvalue", "df", 
                                                   "se", "labeling", "adj.pvalue", 
                                                   "trueLog2FC", "contrast_truth", "protadj"))
adj_spike_limma$Adjustment <- "protein adjustment"
adj_spike_limma$Model <- "Limma"

@@

spike[spike$label == 'mix1-mix2'][['contrast_truth']] <- "LogFC: -1 (mix2-mix1)"
spike[spike$label == 'mix1-mix3'][['contrast_truth']] <- "LogFC: 1 (mix3-mix1)"
spike[spike$label == 'mix1-mix4'][['contrast_truth']] <- "LogFC: 0 (mix4-mix1)"
spike[spike$label == 'mix2-mix3'][['contrast_truth']] <- "LogFC: 2 (mix3-mix2)"
spike[spike$label == 'mix2-mix4'][['contrast_truth']] <- "LogFC: 1 (mix4-mix2)"
spike[spike$label == 'mix3-mix4'][['contrast_truth']] <- "LogFC: -1 (mix4-mix3)"

spike[spike$Label == 'mix3-mix4'][["Label"]] = "mix4 vs mix3"
spike[spike$Label == 'mix2-mix4'][["Label"]] = "mix4 vs mix2"
spike[spike$Label == 'mix1-mix4'][["Label"]] = "mix4 vs mix1"
spike[spike$Label == 'mix2-mix3'][["Label"]] = "mix3 vs mix2"
spike[spike$Label == 'mix1-mix3'][["Label"]] = "mix3 vs mix1"
spike[spike$Label == 'mix1-mix2'][["Label"]] = "mix2 vs mix1"

spike[spike$Label == "mix3 vs mix2" & 
        spike$Model == "T-test"][["trueLog2FC"]] = 2
spike[spike$Label == "mix3 vs mix2" & 
        spike$Model == "T-test"][["log2FC"]] = spike[
          spike$Label == "mix3 vs mix2" & 
        spike$Model == "T-test"][["log2FC"]] * -1
spike[spike$Label == "mix4 vs mix2" & 
        spike$Model == "T-test"][["trueLog2FC"]] = 1
spike[spike$Label == "mix4 vs mix2" & 
        spike$Model == "T-test"][["log2FC"]] = spike[
          spike$Label == "mix4 vs mix2" & 
        spike$Model == "T-test"][["log2FC"]] * -1
spike[spike$Label == "mix4 vs mix3" & 
        spike$Model == "T-test"][["trueLog2FC"]] = -1
spike[spike$Label == "mix4 vs mix3" & 
        spike$Model == "T-test"][["log2FC"]] = spike[
          spike$Label == "mix4 vs mix3" & 
        spike$Model == "T-test"][["log2FC"]] * -1

spike[spike$Label == "mix3 vs mix2" & 
        spike$Model == "Limma"][["trueLog2FC"]] = 2
spike[spike$Label == "mix4 vs mix2" & 
        spike$Model == "Limma"][["trueLog2FC"]] = 1
spike[spike$Label == "mix4 vs mix3" & 
        spike$Model == "Limma"][["trueLog2FC"]] = -1

png("../supplementary/sim_new/spike_in_fc.png", width = 750, height = 500)
spike %>% mutate(Comparison = str_split(contrast_truth, " ", simplify = TRUE)[,1],
      Model = factor(Model, levels=c("Proposed", "Limma", "T-test"))) %>%
  filter(!Label %in% c("mix1-mix2", "mix3-mix4")) %>% 
  ggplot() + 
  geom_boxplot(aes(x = Label, y = log2FC, fill = Model)) + 
  geom_point(aes(y = trueLog2FC, x = Label, color = color_label), 
             shape = 4, size = 4, stroke = 2) + 
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(name = "", values="red", label="True LogFC") + 
 facet_wrap(.~Adjustment) + 
    theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust=1, vjust = 1, size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=18),
       axis.title.y = element_text(size = 18),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 18),
       legend.position = "bottom") + 
  labs(title = "Fold Change of Spike-in Peptides", x = "Comparison with Expected FC")
dev.off()

spike
setDT(spike)[,list(IQR=IQR(log2FC, na.rm = TRUE)),by=list(Model, Label, protadj)] %>% 
  filter(Label %in% c('mix2-mix3', 'mix1-mix3', 'mix1-mix4', 'mix2-mix4') & 
           protadj == 'protein adjustment') %>% 
  group_by(Model) %>% summarize(mean(IQR))

(0.7557581 - 1.1954719) / 1.1954719
(0.7557581 - 1.1277441) / 1.1277441

>>>>

png("../main/images/spike_in_volcano.png", width = 750, height = 500)
combo_plot_df %>% arrange(Model, labeling) %>% 
  filter(abs(log2FC) < Inf & Label %in% c("mix3 vs mix2",
                                          "mix4 vs mix2")) %>%
  ggplot(aes(log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.2, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  geom_vline(aes(xintercept = trueLog2FC),color = "darkred", linetype= "dashed") +
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ Model + contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  scale_y_continuous(limits = c(0,3)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) +
  labs(title = "SpikeIn VolcanoPlot", x= "Log2FC")
dev.off()

@@

@@

# Volcano plot
png("../supplementary/sim_new/spike_in_anova_volcano.png", width = 1000, height = 500)
anova_results %>% arrange(labeling) %>% 
  filter(is.finite(log2FC)) %>%
  ggplot(aes(log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.1, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0, linetype = "dashed") + 
  geom_vline(xintercept = 0) + 
  geom_vline(aes(xintercept = trueLog2FC),color = "darkred", linetype= "dashed") +
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 14), 
       axis.text.y = element_text(size = 14), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  # scale_y_continuous(limits = c(0,1.5)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) + 
  labs(title = "Anova VolcanoPlot")
dev.off()
```

@@

unadj_spike_ttest <- anova_results %>% filter(labeling == "SpikeIn Peptides" & protadj == "no adjustment")
unadj_spike_ttest <- setNames(unadj_spike_ttest, c("Protein", "Label", "log2FC", "SE", "Tvalue", 
                                                   "pvalue", "protadj", "adj.pvalue", "labeling", 
                                                   "contrast_truth", "trueLog2FC"))

unadj_spike_ttest$Adjustment <- "no adjustment"
unadj_spike_ttest$Model <- "Anova"

adj_spike_ttest <- anova_results %>% filter(labeling == "SpikeIn Peptides" & protadj != "no adjustment")
adj_spike_ttest <- setNames(adj_spike_ttest, c("Protein", "Label", "log2FC", "SE", "Tvalue", 
                                                   "pvalue", "protadj", "adj.pvalue", "labeling", 
                                                   "contrast_truth", "trueLog2FC"))
adj_spike_ttest$Adjustment <- "protein adjustment"
adj_spike_ttest$Model <- "Anova"

unadj_spike_limma <- limma_model$PTM.Model %>% filter(labeling == "heavy")
unadj_spike_limma <- setNames(unadj_spike_limma, c("Protein", "Label", "log2FC", "pvalue", "DF", 
                                                   "SE", "labeling", "adj.pvalue", 
                                                   "trueLog2FC", "contrast_truth", "protadj"))
unadj_spike_limma$Adjustment <- "no adjustment"
unadj_spike_limma$Model <- "Limma"
adj_spike_limma <- limma_model$ADJUSTED.Model %>% filter(labeling == "heavy")
adj_spike_limma <- setNames(adj_spike_limma, c("Protein", "Label", "log2FC", "pvalue", "df", 
                                                   "SE", "labeling", "adj.pvalue", 
                                                   "trueLog2FC", "contrast_truth", "protadj"))
adj_spike_limma$Adjustment <- "protein adjustment"
adj_spike_limma$Model <- "Limma"

@@

png("../supplementary/sim_new/spike_in_fc.png", width = 750, height = 500)
spike %>% mutate(Comparison = str_split(contrast_truth, " ", simplify = TRUE)[,1],
      Model = factor(Model, levels=c("Proposed", "Limma", "Anova"))) %>%
  filter(!Label %in% c("mix1-mix2", "mix3-mix4")) %>% 
  ggplot() + 
  geom_boxplot(aes(x = Label, y = log2FC, fill = Model)) + 
  geom_point(aes(y = trueLog2FC, x = Label, color = color_label), 
             shape = 4, size = 4, stroke = 2) + 
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(name = "", values="red", label="True LogFC") + 
 facet_wrap(.~Adjustment) + 
    theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust=1, vjust = 1, size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=18),
       axis.title.y = element_text(size = 18),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 18),
       legend.position = "bottom") + 
  labs(title = "Fold Change of Spike-in Peptides", x = "Comparison with Expected FC")
dev.off()

spike
setDT(spike)[,list(IQR=IQR(log2FC, na.rm = TRUE)),by=list(Model, Label, protadj)] %>% 
  filter(protadj == 'protein adjustment') %>% 
  group_by(Model) %>% summarize(mean(IQR))

spike_se = setDT(spike)[,list(SE=mean(SE, na.rm = TRUE)),by=list(Model, Label, protadj)] %>% 
  filter(protadj == 'protein adjustment') %>% 
  group_by(Model) %>% summarize(mean(SE))

all_se = setDT(spike)[,list(SE=mean(SE, na.rm = TRUE)),by=list(Model, Label, protadj)] %>% 
  filter(protadj == 'protein adjustment') %>% 
  group_by(Model) %>% summarize(mean(SE))

(0.5984246 - 0.9309134) / 0.9309134
